Growing libraries of concepts with wake-sleep program induction

### 2018-07-31 nips_2018_author_response.tex
SCC typo

\textbf{The evolution of task solutions over time:} %\subsubsection*{The evolution of task solutions over time}
Reviewer 1 asks about the ``evolution of solutions to a fixed task through the iterations of the main algorithm.''
In most cases the solution to a fixed task
stays the same,
modulo rewriting the solution in terms of new subroutines.
There are interesting cases however where the
semantics of the program changes as the algorithms constructs more subroutines. Figure~1
illustrates one case for turtle graphics.
\begin{SCfigure}[2][h]
  \centering
  \includegraphics[width=7cm]{figures/rebutal/spirals.eps}
  \caption{Three turtle graphics tasks: the task is to write a program that draws the image. Initially SSC solves the leftmost task without using a loop, but after solving the middle and rightmost tasks,
  it constructs a parametric `spiral' subroutine, which uses a loop -- on subsequent iterations it solves the leftmost task using the `spiral' routine.}
\end{SCfigure}

>>>>

\textbf{The evolution of task solutions over time:} %\subsubsection*{The evolution of task solutions over time}
Reviewer 1 asks about the ``evolution of solutions to a fixed task through the iterations of the main algorithm.''
In most cases the solution to a fixed task
stays the same,
modulo rewriting the solution in terms of new subroutines.
There are interesting cases however where the
semantics of the program changes as the algorithms constructs more subroutines. Figure~1
illustrates one case for turtle graphics.
\begin{SCfigure}[2][h]
  \centering
  \includegraphics[width=7cm]{figures/rebutal/spirals.eps}
  \caption{Three turtle graphics tasks: the task is to write a program that draws the image. Initially SCC solves the leftmost task without using a loop, but after solving the middle and rightmost tasks,
  it constructs a parametric `spiral' subroutine, which uses a loop -- on subsequent iterations it solves the leftmost task using the `spiral' routine.}
\end{SCfigure}
